Pillar 2 - Topic Modeling

### 2019-01-17 Pillar 2 - Topic Modeling.Rmd

```{r compute_tf_idf, cache = TRUE}
compute_tf_idf <- function(data) data %>%
                                   count(Code, word) %>%
                                   bind_tf_idf(term = word, document = Code, n = n)

tf_idf_description <- compute_tf_idf(filter(d_description, `Calendar Year` == "2018-2019"))
tf_idf_overview    <- compute_tf_idf(filter(d_overview, `Calendar Year` == "2018-2019"))
tf_idf_manual      <- compute_tf_idf(d_manual)

@@

  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
  print(g)

@@

  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)
  print(g)

@@

## Course Level
```{r tf-idf course, out.height=8, out.width=16, cache = TRUE}
prepare_tf_idf_course <- function(data) data %>%
                                          filter(Code %in% sample(unique(.$Code), size = 25, replace = F)) %>% # random selection of courses
                                          rename(facet = Code) %>%
                                          group_by(facet) %>%
                                            filter(n >= 2) %>%
                                            top_n(10, tf_idf) %>%
                                          ungroup

@@

## Cluster Level
```{r tf-idf cluster, cache = TRUE}
prepare_tf_idf_cluster <- function(data) data %>%
                                           left_join(select(d_course, Code, Cluster), by = "Code") %>%
                                           filter(!is.na(Cluster)) %>%
                                           rename(facet = Cluster) %>%
                                           group_by(facet, word) %>%
                                             summarise(tf_idf = sum(tf_idf),
                                                       n = sum(n)) %>%
                                             filter(n >= 10) %>%
                                             top_n(10, tf_idf) %>%
                                           ungroup

@@

## Concentration Level
```{r tf-idf concentration, cache = TRUE}
prepare_tf_idf_concentration <- function(data) data %>%
                                                 left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
                                                 filter(!is.na(Concentration)) %>%
                                                 gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                                 rename(facet = Concentration) %>%
                                                 group_by(facet, word) %>%
                                                   summarise(tf_idf = sum(tf_idf),
                                                             n = sum(n)) %>%
                                                   filter(n >= 10) %>%
                                                   top_n(10, tf_idf) %>%
                                                 ungroup

@@

# LDA
## Fitting Model
```{r my_cast_tdm}
my_cast_tdm <- function(data, level) data %>%
  count(Code, word) %>%
  cast_dtm(Code, word, n)

@@

## Results
```{r LDA prepare}
prepare_data_LDA_beta <- function(results) tidy(results, matrix = "beta") %>%
                                        mutate(topic = paste("Topic", topic)) %>%
                                          group_by(topic) %>%
                                            top_n(10, beta) %>%
                                          ungroup %>%
                                          arrange(topic, desc(beta))

@@

  data_gamma <- tidy(results, matrix = "gamma") %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(Code = document)

  if(ensym(level) == sym("Course")) data_gamma <- data_gamma %>%
                                      rename(facet = Code)

  if(ensym(level) == sym("Cluster")) data_gamma <- data_gamma %>% 
                                       left_join(select(d_course, Code, Cluster), by = "Code") %>%
                                       filter(!is.na(Cluster)) %>%
                                       rename(facet = Cluster)

  if(ensym(level) == sym("Concentration")) data_gamma <- data_gamma %>%
                                             left_join(select(d_course, Code, Concentration, `Concentration (additional)`), by = "Code") %>%
                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                             rename(facet = Concentration)

>>>>

```{r compute_tf_idf, cache = TRUE}
compute_tf_idf <- function(data) data %>%
                                   count(`Course ID`, word) %>%
                                   bind_tf_idf(term = word, document = `Course ID`, n = n)

tf_idf_description <- compute_tf_idf(filter(d_description, `Academic Year` == "2018-2019"))
tf_idf_overview    <- compute_tf_idf(filter(d_overview, `Academic Year` == "2018-2019"))
tf_idf_manual      <- compute_tf_idf(d_manual)

@@

  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Plots", width = 16, height = 8)

@@

  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Plots", width = 16, height = 8)

@@

## Course Level
```{r tf-idf course, out.height=8, out.width=16, cache = TRUE}
prepare_tf_idf_course <- function(data) data %>%
                                          filter(`Course ID` %in% sample(unique(.$`Course ID`), size = 25, replace = F)) %>% # random selection of courses
                                          rename(facet = `Course ID`) %>%
                                          group_by(facet) %>%
                                            filter(n >= 2) %>%
                                            top_n(10, tf_idf) %>%
                                          ungroup

@@

## Cluster Level
```{r tf-idf cluster, cache = TRUE}
prepare_tf_idf_cluster <- function(data) data %>%
                                           left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
                                           filter(!is.na(Cluster)) %>%
                                           rename(facet = Cluster) %>%
                                           group_by(facet, word) %>%
                                             summarise(tf_idf = sum(tf_idf),
                                                       n = sum(n)) %>%
                                             filter(n >= 10) %>%
                                             top_n(10, tf_idf) %>%
                                           ungroup

@@

## Concentration Level
```{r tf-idf concentration, cache = TRUE}
prepare_tf_idf_concentration <- function(data) data %>%
                                                 left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
                                                 filter(!is.na(Concentration)) %>%
                                                 gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                                 rename(facet = Concentration) %>%
                                                 group_by(facet, word) %>%
                                                   summarise(tf_idf = sum(tf_idf),
                                                             n = sum(n)) %>%
                                                   filter(n >= 10) %>%
                                                   top_n(10, tf_idf) %>%
                                                 ungroup

@@

# LDA
## Fitting Model
```{r my_cast_tdm}
my_cast_tdm <- function(data, level) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

## Results
```{r LDA prepare}
prepare_data_LDA_beta <- function(results){

  tidy(results, matrix = "beta") %>%
    mutate(topic = paste("Topic", topic)) %>%
      group_by(topic) %>%
        top_n(10, beta) %>%
      ungroup %>%
      arrange(topic, desc(beta))

@@

  data_gamma <- tidy(results, matrix = "gamma") %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(`Course ID` = document)

  if(ensym(level) == sym("Course")) data_gamma <- data_gamma %>%
                                      rename(facet = `Course ID`)

  if(ensym(level) == sym("Cluster")) data_gamma <- data_gamma %>% 
                                       left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
                                       filter(!is.na(Cluster)) %>%
                                       rename(facet = Cluster)

  if(ensym(level) == sym("Concentration")) data_gamma <- data_gamma %>%
                                             left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
                                             gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                             rename(facet = Concentration)
